\chapter{EVALUATION}
This chapter presents the process of evaluating the effectiveness of the whole system and its features. At the same time, self-assessment of the work done by the group, from which the development direction of the topic
\section{Social media website}
\subsection{Evaluation metric}
\subsubsection{Website Grader powered by HubSpot}
This tool evaluate a website based on 4 criteria: performance, mobile, SEO, security.\\
\textbf{Overall}\\
The social media website is scored:
\begin{itemize}
\item Performance: 22/30
\item Mobile: 30/30
\item SEO: 10/30
\item Security: 10/10
\end{itemize}
Compared to \textit{9gag} which is a well known social media for entertainment. 
\begin{table}[H]
\begin{tabular}{|l|c|l|}
\hline
            & \multicolumn{1}{l|}{The social media website} & 9gag  \\ \hline
Performance & 22/30                                         & 24/30 \\ \hline
Mobile      & 30/30                                         & 30/30 \\ \hline
SEO         & 10/20                                         & 30/30 \\ \hline
Security    & 10/10                                         & 10/10 \\ \hline
\end{tabular}
\end{table}
This result is acceptable because 9gag has grown and improved for a lengthy duration since it first launched in 2008. In contrast, the social media website has just been developed for a short amount of time.\\
\textbf{Performance}\\
\begin{itemize}
\item Page size: The heavier the site page, the slower the load.
\item Page request: The more HTTP requests your website makes, the slower it becomes.
\item Page speed: Load time
\item Browser caching: Browser caching speeds up your website by storing frequently used content in local memory.
\item Page redirect: Page redirects add an additional loading cycle, increasing the time to display the page.
\item Compression: When your JavaScript and CSS are properly compressed, it makes your website run much faster.
\item Render blocking: Remove or defer JavaScript and CSS that interferes with loading above-the-fold content.
\begin{table}[H]
\begin{tabular}{|c|c|c|}
\hline
                & The social media website & 9gag              \\ \hline
Page size       & 715 KB                   & 337 KB            \\ \hline
Page requests   & 34                       & 74                \\ \hline
Page speed      & 0.4                      & 0.5               \\ \hline
Browser caching & \checkmark               & \checkmark        \\ \hline
Page redirects  & No page redirects        & No page redirects \\ \hline
Compression     & $\times$                 & \checkmark        \\ \hline
Render blocking & $\times$                 & $\times$            \\ \hline
\end{tabular}
\end{table}
\end{itemize}
\textbf{Mobile}\\
Responsive design gives the social media the ability to scale on different device types which also enable mobile friendliness.\\
\textbf{SEO}\\
\begin{itemize}
\item Page title: Page titles should be no longer than 70 characters in length and not repeat keywords.
\item Meta description: Meta descriptions should be no longer than 300 characters in length and should be relevant to the page.
\item Headings: Heading tags distinguish headings from core page content.
\item Sitemap: Site maps help users navigate your site quickly and easily.
\end{itemize}
\begin{table}[H]
\begin{tabular}{|c|c|c|}
\hline
                 & The social media website & 9gag \\ \hline
Page titles      & \checkmark               & \checkmark  \\ \hline
Meta description & $\times$                 & \checkmark  \\ \hline
Headings         & $\times$                 & \checkmark  \\ \hline
Sitemap          & $\times$                 & \checkmark  \\ \hline
\end{tabular}
\end{table}
In this project, marketing is not focused on, this result is inevitable.
\textbf{Security}\\
SSL certificates protect the social media website from attacks and give visitors confidence that your site is authentic and trustworthy.
\subsection{Result}
\section{Video classifier}
\subsection{Evaluation metric}
\subsection{Result}


